\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-11-09 paper.Rmd
recompiled and fixed 0.95 to 0.99 in Bolts

$W$ in equation \@ref(eq:velocity-time) represents Lambert's W function [@R-LambertW]. MSS and TAU parameters are estimated using `model_using_splits` function:

@@

```{r}
bolt_model <- bolt_model %>%
  group_by(model) %>%
  mutate(
    dist_95_MSS = find_velocity_critical_distance(
      MSS = MSS, TAU = TAU, 
      #time_correction = time_correction, 
      #distance_correction = distance_correction,
      percent = 0.99
    ),
   time_95_MSS = find_velocity_critical_time(
      MSS = MSS, TAU = TAU, 
      time_correction = time_correction, 
      percent = 0.99
    )
  )

>>>>

$W$ in equation \@ref(eq:time-distance) represents Lambert's W function [@R-LambertW]. MSS and TAU parameters are estimated using `model_using_splits` function:

@@

```{r}
bolt_model <- bolt_model %>%
  group_by(model) %>%
  mutate(
    dist_99_MSS = find_velocity_critical_distance(
      MSS = MSS, TAU = TAU, 
      #time_correction = time_correction, 
      #distance_correction = distance_correction,
      percent = 0.99
    ),
   time_99_MSS = find_velocity_critical_time(
      MSS = MSS, TAU = TAU, 
      #time_correction = time_correction, 
      percent = 0.99
    )
  )

### 2020-11-09 paper.tex
recompiled and fixed 0.95 to 0.99 in Bolts

\(W\) in equation \eqref{eq:velocity-time} represents Lambert's W function \citep{R-LambertW}. MSS and TAU parameters are estimated using \texttt{model\_using\_splits} function:

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bolt_model <- bolt_model %>%
+   group_by(model) %>%
+   mutate(
+     dist_95_MSS = find_velocity_critical_distance(
+       MSS = MSS, TAU = TAU, 
+       #time_correction = time_correction, 
+       #distance_correction = distance_correction,
+       percent = 0.99
+     ),
+    time_95_MSS = find_velocity_critical_time(
+       MSS = MSS, TAU = TAU, 
+       time_correction = time_correction, 
+       percent = 0.99
+     )
+   )
R> 
R> bolt_model[c(1, 8, 9)]
\end{CodeInput}
\begin{CodeOutput}
#> # A tibble: 6 x 3
#> # Groups:   model [6]
#>   model                    dist_95_MSS time_95_MSS
#>   <chr>                          <dbl>       <dbl>
#> 1 No correction                   68.7        7.20
#> 2 No correction - RT              51.1        5.73
#> 3 Time correction                 51.0        5.72
#> 4 Time correction - RT            51.0        5.54
#> 5 Distance correction             35.8        4.75
#> 6 Distance correction - RT        35.8        4.57
\end{CodeOutput}
\end{CodeChunk}

>>>>

\(W\) in equation \eqref{eq:time-distance} represents Lambert's W function \citep{R-LambertW}. MSS and TAU parameters are estimated using \texttt{model\_using\_splits} function:

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bolt_model <- bolt_model %>%
+   group_by(model) %>%
+   mutate(
+     dist_99_MSS = find_velocity_critical_distance(
+       MSS = MSS, TAU = TAU, 
+       #time_correction = time_correction, 
+       #distance_correction = distance_correction,
+       percent = 0.99
+     ),
+    time_99_MSS = find_velocity_critical_time(
+       MSS = MSS, TAU = TAU, 
+       #time_correction = time_correction, 
+       percent = 0.99
+     )
+   )
R> 
R> bolt_model[c(1, 8, 9)]
\end{CodeInput}
\begin{CodeOutput}
#> # A tibble: 6 x 3
#> # Groups:   model [6]
#>   model                    dist_99_MSS time_99_MSS
#>   <chr>                          <dbl>       <dbl>
#> 1 No correction                   68.7        7.20
#> 2 No correction - RT              51.1        5.55
#> 3 Time correction                 51.0        5.54
#> 4 Time correction - RT            51.0        5.54
#> 5 Distance correction             35.8        3.94
#> 6 Distance correction - RT        35.8        3.94
\end{CodeOutput}
\end{CodeChunk}
